---
title: "2 minute introduction"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{2 minute introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(knitr)
```

```{r}
library(odktidy)
```

## Example input

This example data is included in the `odktidy` package

```{r, eval = FALSE}
head(example_data)
```

```{r, echo = FALSE}
head(example_data) %>% (knitr::kable)
```


```{r, eval = FALSE}
head(example_questions)
```

```{r, echo = FALSE}
head(example_questions) %>% (knitr::kable)
```


```{r, eval = FALSE}
head(example_choices)
```

```{r, echo = FALSE}
head(example_choices) %>% (knitr::kable)
```

## Create odk data frame


```{r, warning=FALSE}

myodk <- as_odk(example_data,example_questions,example_choices)

```


At the base, an odk object is just a regular tibble (data.frame); you can use it like any other data frame:

```{r,eval=FALSE}
head(myodk)
```

```{r, echo = FALSE}
head(myodk) %>% kable
```


```{r}
typeof(myodk)
class(myodk)

nrow(myodk)
ncol(myodk)
myodk[200,20]

```

## Vector classes

odk tibbles have special vector types for select_one and select_multiple questions (imported from the 'categorical' package; see `browseVignettes("categorical")` for details)


For select multiple, the concatenated and logical columns for each choice are gone, instead there is one column of type select_multiple:

```{r}
head(myodk[,23])
```


```{r}
#
# myodk[,20:30]
#
# on_select_multiple<-function(x,f,...){
#   out<-purrr::pmap(c(list(x),list(...)),f)
#   if(all(unlist(purrr:::map(out,length))==1)){
#     unlist(out)
#   }
# }
# library(tidyr)
# library(dplyr)
# myodk %>% categorical::mutate_select_multiple(new = 'mother' %in% household_expenditure) %>% select(new)
#
# on_select_multiple(myodk$household_expenditure,function(x){'mother' %in% x})
# unnest(as.list(myodk$household_expenditure[1:10]))
#
# spread_select_multiple<-function(x){
#   unique_values<-purrr::map(x,levels) %>% unlist %>% unique
#   spread<-purrr::map(x,function(x){
#
#       !is.na(match(unique_values, x))
#
#   }) %>% do.call(rbind,.)
#   colnames(spread)<-unique_values
#   spread
# }
# x<-as.logical(myodk$household_expenditure)
# colnames(matrix(T,T))
#
#
# gather_select_multiple<-function(x){
#   assertthat::assert_that(is.matrix(x))
#   assertthat::assert_that(is.logical(x))
#   assertthat::assert_that(!any(duplicated(colnames(x))),
#                           msg = 'to gather a logical matrix to a select multiple column, column names must be unique')
#
#   assertthat::assert_that(!any(is.null(colnames(x))),msg = 'x must have column names')
#
#   choices<-colnames(x)
#   apply(x,1,function(x){
#     names(which(x))
#   })  %>%  as_select_multiple(choices = choices)
#
#   }
#
#
# c(factor('hello'),'world')
# class(myodk$household_expenditure[[3]])
#
# myodk$household_expenditure[[2]] %<>% c('father')
# myodk$household_expenditure[1:3]
# rm(select_multiple)
# as_select_multiple(x) %>% head
# traceback()
#
#
#
#
# myodk$household_expenditure<- myodk$household_expenditure %>% spread_select_multiple
#
# myodk$household_expenditure %>% unnest
#
# devtools::install_github("mabafaba/composr")
#
# myodk %>% rowwise %>%
#   mutate_select_multiple(he_ln = composr:::selected_exactly_lgl('mother', household_expenditure) ) %>%
#   select(household_expenditure,he_ln) %>% .[20:30,]
#
#
#
# composr::sm_selected(myodk)
#
# myodk %>% mutate_select_multiple(length(household_expenditure)) %>% select(household_expenditure,he_ln) %>% .[20:30,]
#
#
#
#
#
# `%has all of%` <-composr:::selected_all_lgl
# `%has exactly%`<-composr:::selected_exactly_lgl
# `%has any of%`<-composr:::selected_any_lgl
# `%has none of%` <-composr:::selected_none_lgl
#
#
# myodk %>% mutate_select_multiple(hasf = household_expenditure %has exactly% c( 'mother'))  %>%
#   select(household_expenditure,hasf) %>% .[20:30,]
#
# library(forcats)
#
# somedata$household_expenditure %>% levels
#
# levels.odk_select_multiple<-function(x){
#   c(lapply(x,levels) %>% unlist,
#     lapply(x,as.character) %>% unlist) %>% unique
# }
#
# somedata<-myodk[48:53,23]
#
# somedata
# fct_collapse.
# levels(somedata$household_expenditure)
#
# somedata %>% mutate_select_multiple(
#   any_male_selected = any(
#     grep('father|male', household_expenditure)
#     )
#   )
#
#
# as.logical(somedata$household_expenditure)
#
#
#
#
#
# label<-function(x){
#   UseMethod("label")
# }
# class(somedata$household_expenditure)
#
# myodk$household_expenditure
#
#
# myodk<-as_odk(df,questions,choices)
# myodk[-(1:20),-(1:20)]
#
#
# myodk$household_expenditure[100:110]
# q<-attributes(myodk)$questionnaire
# q$question_get_choices('household_expenditure')dev
#
#
#
# debug(q$question_is_sm_choice)
#
# q$question_is_sm_choice('household_expenditure.adult_female')
#

```
